---
title: "Spatial Krill catches from Kawaguchi & Nicol 2020"
author: "Andrew Constable"
date: "15/07/2020"
output: html_document
---

This document describes the process and displays results for extracting the spatial krill catches from decadal maps in Kawaguchi & Nicol 2020.  These spatial maps represent the catches in each decade for which the location could be assigned.  They do not represent the total catch in each decade.  

The process involves the following steps:
     Step 1: Clean up and prepare figures with data
     Step 2: Import PNG images to Manifold to geocode pixels and output data
     Step 3: In Manifold, query the image output for the catch data
     Step 4: Using R, determine cell attributes and save data

The result is a saved R list - one image per decade, containing, for each fished cell in each decadal map, the cell center (longitude, latitude), the catch category in tonnes (log10 scale), and the MEASO area in which it resides, and the CCAMLR ASD (Area, Subarea or Division).


```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Input data

WorkDir<-'C:\\_w\\_d\\Catch\\'

# Generate dataframe with image data
CatchDecade<- c(1970, 1980,1990,2000,2010)
CatchFilename<-paste("Catch - ",CatchDecade,"s.csv",sep="")  # ensure in WorkDir
CatchTitle<-paste("Krill Catch data - ",CatchDecade,"s",sep="")

# Shapefiles for plotting and for assigning data
AntarcticaShapeFile<-"C:\\_w\\maps\\shapefiles\\Antarctic coastline\\Aad_coastline Drawing.shp" 
SubAntarcticIslandsShapefile<-"C:\\_w\\maps\\shapefiles\\subantarctic_islands\\gshhs_f_30-60s.shp"
MEASOshapefile<-"C:\\_w\\maps\\shapefiles\\Measo_areas_shapefiles\\Measo_areas_shapefiles.shp"
CCAMLRshapefile<-"C:\\_w\\maps\\shapefiles\\CCAMLR\\asd-shapefile-WGS84\\asd-shapefile-WGS84.shp"

# RGB colour codes for the different shades of cells in the krill maps

RGBcategories<-matrix(c(0, 255, 255, 255
                       ,1, 204, 204, 204
                       ,2, 153, 153, 153
                       ,3, 101, 101, 101
                       ,4,  50,  50,  50
                       ,5,   0,   0,   0),ncol=4,byrow=TRUE)

dimnames(RGBcategories)[[2]]<-c("Catch","Red","Green","Blue")

# Krill catch in tonnes assigned to each category
#    - based on mid-point of log10 scale
#    - last category was capped at 615,400 tonnes

KrillCatchCategories<-matrix(c(0,      5
                              ,1,     50
                              ,2,    500
                              ,3,   5000
                              ,4,  50000
                              ,5, 350000),ncol=2,byrow=TRUE)

dimnames(RGBcategories)[[2]]<-c("Catch","Red","Green","Blue")

# Each cell will have many pixels from the PNG file.  
# The code samples a proportion of the cell from its mid-point, 
# thereby avoiding noisy colours at the boundary.
# Inputs are the dimensions of the cell in degrees longitude and latitude.
# The proportion to be sampled is called the tolerance for longitude and latitude.

Cell_Long<-2 # degrees longitude
Cell_Lat<-1  # degrees latitude
Cell_Long_Tol<-0.6
Cell_Lat_Tol<-0.6



# Libraries

library(sf)
library(ggplot2)
library(rgdal)


# Functions

# function to determine the cells in the data set that have a specified 
# catch category

GridCellCatch<-function(CatchCat        # category value for the catch
                       ,Data            # data from file exported from Manifold
                       ,RGBcategories   # one record per catch category with RGB values
                       ,Tol_long        # max degrees in longitude from centre point to be included
                       ,Tol_lat         # same for latitude
                       ){ # begin function

  RGB<-RGBcategories[RGBcategories[,"Catch"]==CatchCat,]
  CD<-Data[ Data[,"Red"]==RGB["Red"] & Data[,"Green"]==RGB["Green"] & Data[,"Blue"]==RGB["Blue"]
           ,c("Long","Lat")] 

  # change Long and Lat to the grid cell centres where cell values are min<= centre < max 
     CD[CD[,"Long"]==180,"Long"] <- (-180)  # correct the anti-prime meridian so as will be in a cell
     
     GridLong <- floor(CD[,"Long"]/2)*2+1    
     GridLong[abs(CD[,"Long"]-GridLong)>Tol_long] <- NA

     GridLat  <- floor(CD[,"Lat"])+0.5 
     GridLat[(abs(CD[,"Lat"]-GridLat)>Tol_lat)] <- NA
     Keep<-!is.na(GridLong) & !is.na(GridLat)
     if(sum(Keep)>0){
        res<-aggregate(GridLong[Keep],list(GridLong[Keep],GridLat[Keep]),length)
        res<-cbind(res[,c(1,2)],rep(CatchCat,nrow(res)),res[,3])
        dimnames(res)[[2]] <- c("Long","Lat","Catch","Pixels")
     } else res<-NULL
     
   return(res)
           } # end function

```
  
**Step 1: Clean up and prepare figures with data**
  
In an image processing package (e.g. Illustrator):  
  
Place red dots in positions on figure for georeferencing.  For equal area  projections, dots evenly spaced around the perimeter are all that is needed.  Here I used:  
     483nw = northwest corner of Subarea 48.3  
     586nw = northwest corner of Subarea 58.6  
     5851ne = northeast corner of Division 58.5.1  
     5841ne = northeast corner of Division 58.4.1  
     882nw = northwest corner of Subarea 88.2  
     882ne = northeast corner of Subarea 88.2  
  
Export image.  
  
In image processing package (e.g. Photoshop):  
  
Remove all unwanted colours.  I used the Magic Wand tool to rapidly bound areas and 'delete'.  Remove all background from within ASD lines and within the continent.  Be careful not to delete polygons of catch data.  Use erasor tool to then delete all coastlines, islands and ASD lines.  Be careful not to remove too much colour from within catch polygons.  
  
Once all background lines and colours have been removed, use magic wand tool to select all background (may need to do this in areas bounded by catch polygons as well) and replace with a colour not used in the catch colour ramp by using Paint Bucket tool e.g. yellow.  This background colour is needed for differentiating background from catch polygons (Manifold assigns 'white' to pixels without colour)  
  
Use eyedropper tool to sample colours in order to verify (and note) the RGB numerical combination - these are needed for the algorithm.  
  
Save and export to PNG file  
    
**Step 2: Import PNG images to Manifold to geocode pixels**  
  
Import PNG image to Manifold as an image.  Add control points at the red georeferencing dots, using same names as georeferencing control points on the base map.  Then georeference to the base map.  
  
    
**Step 3: In Manifold, query the image output for the catch data**  
  
Use a query in manifold to obtain all the data for each pixel.  
e.g. SELECT * FROM [Fig.6.4 v1 2010-2019 with background] WHERE [Latitude (I)] < (-45);  
  
Export table as a CSV file saving at least the longitude and latitude of the pixel and the Red, Green and Blue colours.  This data are the minimum requirements for the processing algorithm.  
  
  
**Step 4: Using R, determine cell attributes and save data**  
  
Partitions for historical krill catches are based on decadal reporting provided by CCAMLR Secretariat in 6 x log10 categories of total catch weight over each decade in areas 2 degree longitude (centres at odd numbers) by 1 degree latitude (centres at 0.5 of each degree).  
  

```{r CatchData, echo=FALSE, message=FALSE}

setwd(WorkDir)

KrillDecadalCatches<-NULL  # for saving object at end

# loop through all images

for (i in 1:length(CatchFilename)){

CatchData<-read.csv2(CatchFilename[i], header = TRUE, sep = ",", dec = ".")

# keep only relevant variables in correct order and rename variables
dCatch<-CatchData[,c("Center.Longitude..I.","Center.Latitude..I.","Red..I.","Green..I.","Blue..I.")]
dimnames(dCatch)[[2]]<- c("Long","Lat","Red","Green","Blue")

# tolerance settings as maximum distance from centre of grid cell 
#  required to be valid otherwise return NA for grid cell
Tol_long<-Cell_Long*Cell_Long_Tol/2  # in degrees longitude
Tol_lat<-Cell_Lat*Cell_Lat_Tol/2   # in degrees latitude


Res<-lapply(RGBcategories[,"Catch"],GridCellCatch
                                   ,dCatch         # data imported from Manifold
                                   ,RGBcategories   # one record per catch category with RGB values
                                   ,Tol_long        # max degrees in long from centreto be included
                                   ,Tol_lat         # same for latitude)
                                    ) # end sapply
CellCatch<-do.call(rbind, Res)  # merges all lists into a data.frame
CatchCatPresent<-unique(CellCatch[,"Catch"])


# plot results for checking  


# Catch data

g <- raster::rasterFromXYZ(CellCatch[,c("Long","Lat","Catch")])
p <- raster::rasterToPolygons(g)

## now sf - project polygons
pp <- sf::st_segmentize(sf::st_as_sf(p), 0.1)  ## segmentize so curvy
pp <- sf::st_set_crs(pp, 4326)  ## longlat/WGS84

# Antarctic coastline

cst <- sf::read_sf(AntarcticaShapeFile)
cst <- sf::st_set_crs(cst, 4326)

sai <- sf::read_sf(SubAntarcticIslandsShapefile)
sai <- sf::st_set_crs(sai, 4326)

ccamlr <- sf::read_sf(CCAMLRshapefile)
ccamlr <- sf::st_set_crs(ccamlr, 4326)

prj <- "+proj=laea +lon_0=0 +lat_0=-90 +datum=WGS84"
crs <- sf::st_crs(prj)

# in order to achieve a colour scale appropriate across all maps in series
Colours<-gray.colors(6, start = 1, end = 0)
ColMin<-Colours[(min(CatchCatPresent)+1)]
ColMax<-Colours[(max(CatchCatPresent)+1)]

KrillImage<-ggplot(st_transform(pp, crs), aes(fill = Catch)) + geom_sf()  + geom_sf(data = ccamlr, aes(fill= NULL), fill = NA, color="red") + geom_sf(data = cst, aes(fill = NULL, lwd=NULL)) + scale_fill_gradientn(limits=c(0,5),colours=Colours) + ggtitle(CatchTitle[i]) + theme(panel.background = element_rect(fill="light blue"))

print(KrillImage)
ggsave(paste(CatchTitle[i],".png",sep=""),plot=KrillImage)


# Assign cells to MEASO areas


xsf <- sf::st_as_sf(CellCatch, coords = c("Long", "Lat"), crs = 4326)

# where 'd' is your data frame (not a matrix) and coords is the names in longitude,latitude order of the coordinate columns. 
# Then you project to the polygons, 


MEASOareas <- sf::read_sf(MEASOshapefile)
MEASOareas <- sf::st_set_crs(MEASOareas, 4326)

psf <- st_transform(xsf, st_crs(MEASOareas))

# and then get  a grouping with 

join1<-st_join(psf, MEASOareas)

# that will copy 'name' of the measo regions onto that data frame, so then you have a one to one row-identifier for each point. 

ccamlr2<-ccamlr[c(1,3,14)]
csf<-st_transform(join1, st_crs(ccamlr2))

join2<-st_join(csf, ccamlr2)

KrillDecadalCatches<-c(KrillDecadalCatches,list(join2))

} # end image loop

# save data object as list of dataframes

names(KrillDecadalCatches)<-CatchDecade
saveRDS(KrillDecadalCatches,"KrillDecadalCatches.rds") 


```





