---
title: "MEASO - longline effort by ASD for IMAF"
author: "Andrew Constable"
date: "25/10/2020"
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    fig_caption: yes

---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(scales)
library(png) # for grabbing dimensions of png files
library(dplyr)
library(raster)
library(rgdal)
library(maptools)
library(sp)
library(measoshapes) # from GitHub  remotes::install_github("AustralianAntarcticDivision/measoshapes")
library(sf)
library(RColorBrewer)
library(SOmap)  #remotes::install_github("AustralianAntarcticDivision/SOmap")
library(geodist)
library(rgeos)
library(colorspace)


knitr::opts_chunk$set(echo = TRUE)


RootDir<-'/Users/andreworca/Desktop/_wAAD/'
WorkDir<-'/Users/andreworca/Desktop/_wAAD/_d/Catch/'

# Editing and Development Notes:
#
# 1. This code is inherited from "MEASO CCAMLR catch data.rmd" which has the basic analyses testing the data.  
            # The code here strips away the testing routines.
#


source("InputData.R")

BirdCatchData   <-read.csv2(paste(WorkDir,'Seabird bycatch.csv',sep="")
                              , header = TRUE, sep = ",", dec = ".")

# Output flags

plotToothfish<-TRUE
addIUU<-TRUE

# distribution of catches by which areas

AreaGroups<-c("ASD")  # add ASD if need both


# decades for reporting

decade<-seq(1960,2010,10)



################# load functions #####################

source("fnBaseRules.R") # the rules for dividing ASD catch and effort between MEASO areas
source("fnCatch_summary.R")
source("fnDepthArea.R")
source("fnCalcMEASO_TimeSeries_Effort.R")
source("fnCalcMEASO_TimeSeries.R")
source("fnDistributeDepVar.R")

source("fnSetupCatchDistRule.R")
source("fnCatchDistRule.R")
source("fnPropInMareaForRule.R")


fnYmax<-function(m){# m is the maximum catch
  om<-floor(log10(m)) # order of magnitude
 if((m*10^(-om))>5) cInt<-10^om else cInt<-0.5*10^om
 return(c(ceiling(m/cInt)*cInt,cInt))
  } # end function



```


```{r ,echo=FALSE}
# CEdata is the main data frame with effort records

CC_Season<-CEdata[,"Calendar_Year"]
NextYear<-!is.na(CEdata[,"Month"]) & CEdata[,"Month"]>11
CC_Season[NextYear]<-CC_Season[NextYear]+1
Split_Year<-CEdata[,"Calendar_Year"]
NextYear<-!is.na(CEdata[,"Month"]) & CEdata[,"Month"]>6
Split_Year[NextYear]<-Split_Year[NextYear]+1
CEdata<-cbind(CEdata,CC_Season,Split_Year)
```


```{r catch_1, echo=FALSE, eval=FALSE}
# separation of krill catch from fish catch given same effort record.  assume effort was bottom trawling if it was mixed as no data to differentiate.


########################################################################
# modify records to enable use of rules to assign catches to MEASO areas

# NOTE - IF RECORDS ARE MODIFIED TO CHANGE GROUP - MAKE CHANGES IN "B-M Step1.CSV" OR "B-M Step2.CSV" AS REQUIRED 

########
# Case 1: SUN catch in Area 58 in years 1978, 1979.  Has Antarctic krill and Subantarctic fish species. Reassign krill to 
# midwater trawl (not bottom trawl) and krill fishery rather than groundfish fishery

dfSelect <- (CEdata[,"Flag_CTY_Code"]=="SUN" 
          & CEdata[,"GAR_Code"]=="58" 
          & (CEdata[,"Calendar_Year"]=="1978" | CEdata[,"Calendar_Year"]=="1979")
          & CEdata[,"Catch_TXN_Code"]== "KRI")
CEdata[dfSelect,"Target_TXN_Code"] <- "KRI"  # for krill fishery


# Added records to "B-M Step2.csv"  :  
#            OT  SUN  7  58  1978  M
#            OT  SUN  7  58  1979  M

```

# Corrections of data in the Statistical Bulletin

Effort data for longline fishing in 1996 Split-Year from 58.5.1 seems an order of magnitude higher than plausible.  The mean number of hooks per haul for that year was 29,075 compared to a maximum mean for all other years of 9,319 hooks per line. Inspection of the monthly records, including consideration of flag state, the error seems to be for that split year irrespective of flag state.  Dividing by 10 brings the hooks in line with hauls and catches in years before and after that period for the flag states involved.

```{r Corrections, echo=FALSE}
dfSelect<-CEdata[,"GAR_Code"]=="5851" & ((CEdata[,"Calendar_Year"]==1995 & CEdata[,"Month"]>6) |(CEdata[,"Calendar_Year"]==1996 & CEdata[,"Month"]<7)) & CEdata[,"GTY_Code"]=="LLS"
print(CEdata[dfSelect,c("Flag_CTY_Code","Calendar_Year","Month","Target_TXN_Code","Vessel_Count","Haul_Count","Hook_Count")])
CEdata[dfSelect,"Hook_Count"]<-CEdata[dfSelect,"Hook_Count"]/10

```

```{r TargetGroups, echo=FALSE}

TargetFishery<-CSB_taxa[unique(match(CEdata[,"Target_TXN_Code"],CSB_taxa[,"TXN_Code"])),]
TF_Plot_Order<-data.frame(TFn      = c(     3,     2,     8,     1,     7,     6,      1,    2,     1 
                                            ,    6,     1,     5,     9,     1,     2)
                         ,TXN_Code = c( "TOT", "ANI", "SQS", "MZZ", "KRI", "LXX", "NOX", "ICX", "NOG"
                                            ,"ELC", "GHP", "ANS", "KCX", "NOS", "WIC")
                         ,DepthRange = c("600-1800m", "100-700m", "Pelagic", "-", "Pelagic", "Pelagic", "0-500m", "100-650", "0-500m"
                                            ,"Pelagic", "150-350m", "0-700m", "200-1500m", "0-600m", "100-650m")
                          ) # end data frame

TF_Plot_Order<-TF_Plot_Order[order(TF_Plot_Order[,"TFn"]),]

printTF<-data.frame(Fishery    = TF_Names[match(TF_Plot_Order[,"TFn"],TF_Names[,"TFn"]),"Fishery"]
                   ,TaxonCode  = TF_Plot_Order[,"TXN_Code"]
                   ,TaxonName  = CSB_taxa[match(TF_Plot_Order[,"TXN_Code"],CSB_taxa[,"TXN_Code"]),"TXN_Name"]
                   ,Depth      = TF_Plot_Order[,"DepthRange"]
                   ) # end df

# create vector to be added to CEdata for the Target fishery for each record

Fishery_type<-TF_Plot_Order[match(CEdata[,"Target_TXN_Code"],TF_Plot_Order[,"TXN_Code"]),"TFn"]  # plot by number of Target Fishery to get right order 

CEdata<-cbind(CEdata,Fishery_type)
dimnames(CEdata)[[2]][length(names(CEdata))]<-"TFN"
```

```{r GTstep1,echo=FALSE}
# add location following inspection and creating a CSV file with relevant assignment from first step: data_Location_B_M_Step_1
# avoid problems with merge creating row names

dfTmp1<-merge(CEdata,data_Location_B_M_Step_1,by=c("GTY_Code","Flag_CTY_Code","TFN"))

```
  

```{r GTstep2,echo=FALSE}
# modify location following inspection of SUN data for OT and creating a CSV file with relevant assignment from second step: data_Location_B_M_Step_2

dfTmp2<-merge(dfTmp1,data_Location_B_M_Step_2,by=c("GTY_Code","Flag_CTY_Code","TFN","GAR_Code","Calendar_Year"),all.x=TRUE)
dfTmp2[dfTmp2[,"Location.x"]=="U","Location.x"]<-dfTmp2[dfTmp2[,"Location.x"]=="U","Location.y"]
dimnames(dfTmp2)[[2]][dimnames(dfTmp2)[[2]]=="Location.x"]<-"Location"
CEdata<-dfTmp2[,-which(dimnames(dfTmp2)[[2]] %in% "Location.y")]
GTY_rev<-CEdata[,"GTY_Code"]
GTY_rev[GTY_rev=="OT"]<-unlist(lapply(CEdata[GTY_rev=="OT","Location"],function(g){paste("OT",g,sep="")}))
CEdata<-cbind(CEdata,GTY_rev)

remove("dfTmp1")
remove("dfTmp2")
remove("GTY_rev")

```

```{r BottomTrawl_TotalCatch, echo=FALSE}
# deal with no effort data

# merge columns for each record which is the total groundfish+icefish+toothfish catch in order to analyse the 
# proportion of the catch in the year represented by the records with effort information.

CatchTaxa<-c("TOT","TOP","TOA",BFTaxa[which(BFTaxa[,"Catch_Group"] %in% c(1,2,10,15,16)),"Code"],BFTaxa[which(BFTaxa[,"Catch_Group"] %in% c(3,9)),"Code"])

# extract catch data associated with effort records & compare with a total extraction of target catch data

RecordID<-CEdata[,"AFE_ID"]

#subset catch data to include records from effort data and only for CatchTaxa

BottomTrawlCatch<-CSBdata[which(CSBdata[,"AFE_ID"] %in% RecordID),]
BottomTrawlCatch<-BottomTrawlCatch[which(BottomTrawlCatch[,"Catch_TXN_Code"] %in% CatchTaxa),]
BTcatch<-aggregate(BottomTrawlCatch[,"Green_Weight"],list(BottomTrawlCatch[,"AFE_ID"]),sum)

dimnames(BTcatch)[[2]]<-c("AFE_ID","Catch")
CEdata<-merge(CEdata,BTcatch,by="AFE_ID")
#print(CEdata)



```

# Rules for distributing effort between MEASO reporting areas

Effort was distributed amongst MEASO areas according to the rules developed for distributing catch.

```{r MEASOdistributionFunctions,echo=FALSE}
########## Seabed areas #############################################

Seabed_areas <- readRDS(Seabed_file)
# give each cell an area of 2x2 km until it is available in input file
Seabed_areas<-cbind(Seabed_areas,rep(4,nrow(Seabed_areas)))

# rename variables to be consistent with code
dimnames(Seabed_areas)[[2]]<-c("Lon","Lat","Cell","Depth","Iceshelf","MEASO","ASD","SSRU","SSMU","Area")

Cbed_rules<-Seabed_areas[!(Seabed_areas[,"Iceshelf"]) & !is.na(Seabed_areas[,"ASD"]) 
                         & !is.na(Seabed_areas[,"MEASO"]),c("Cell","Lon","Lat","Depth","MEASO","ASD","SSMU","SSRU","Area")]
Cbed_rules[is.na(Cbed_rules[,"SSRU"]),"SSRU"]<-"NA"
Cbed_rules[is.na(Cbed_rules[,"SSMU"]),"SSMU"]<-"NA"

remove(Seabed_areas)  # free up memory
```


# Longlining and Potting Effort

Longlining and potting is combined.  as they both use bottom longline deployments.  the two methods of longline fishing have not been differentiated - Spanish longlines, which tend to float off the bottom once deployed, and integrated weighted lines, which sit on the bottom.

## Longlines

```{r , echo=FALSE}

dLine<-CEdata[CEdata[,"Location"]=="B" & (CEdata[,"GTY_rev"]=="LLS"), ]

EffortRecords<-                    (!is.na(dLine[,"Hook_Count"]) &  is.na(dLine[,"Haul_Count"]) &  is.na(dLine[,"Fishing_Days"]))
EffortRecords<-cbind(EffortRecords,( is.na(dLine[,"Hook_Count"]) & !is.na(dLine[,"Haul_Count"]) &  is.na(dLine[,"Fishing_Days"])))
EffortRecords<-cbind(EffortRecords,( is.na(dLine[,"Hook_Count"]) &  is.na(dLine[,"Haul_Count"]) & !is.na(dLine[,"Fishing_Days"])))
EffortRecords<-cbind(EffortRecords,(!is.na(dLine[,"Hook_Count"]) & !is.na(dLine[,"Haul_Count"]) &  is.na(dLine[,"Fishing_Days"])))
EffortRecords<-cbind(EffortRecords,(!is.na(dLine[,"Hook_Count"]) &  is.na(dLine[,"Haul_Count"]) & !is.na(dLine[,"Fishing_Days"])))
EffortRecords<-cbind(EffortRecords,( is.na(dLine[,"Hook_Count"]) & !is.na(dLine[,"Haul_Count"]) & !is.na(dLine[,"Fishing_Days"])))
EffortRecords<-cbind(EffortRecords,(!is.na(dLine[,"Hook_Count"]) & !is.na(dLine[,"Haul_Count"]) & !is.na(dLine[,"Fishing_Days"])))
# for all NAs
res<-seq(1,nrow(dLine),1)
for(c in 1:ncol(EffortRecords)) res<-res[!EffortRecords[res,c]]
EffortRecords<-cbind(EffortRecords,rep(FALSE,nrow(dLine)))
EffortRecords[res,ncol(EffortRecords)]<-TRUE


cat("Records for Hooks                : ",sum(EffortRecords[,1]),"\n",sep="")
cat("Records for Hauls                : ",sum(EffortRecords[,2]),"\n",sep="")
cat("Records for Days                 : ",sum(EffortRecords[,3]),"\n",sep="")
cat("Records for Hooks & Hauls        : ",sum(EffortRecords[,4]),"\n",sep="")
cat("Records for Hooks & Days         : ",sum(EffortRecords[,5]),"\n",sep="")
cat("Records for Hauls & Days         : ",sum(EffortRecords[,6]),"\n",sep="")
cat("Records for Hooks, Hauls, Days   : ",sum(EffortRecords[,7]),"\n",sep="")
cat("Records for NA in all three      : ",sum(EffortRecords[,8]),"\n",sep="")
cat("Records Total                    : ",nrow(dLine),"\n",sep="")


# save records with missing effort
#write.csv2(dLine[EffortRecords[,8],],"CSB_missing_effort.csv")

# 
```

Number of hooks is a good proxy for the length of the longline.  This is because they are typically set 1m apart.  Less than 5% of longline records (114 out of 2603) do not have hooks associated with them.  These records were not used in this analysis.


```{r , echo=FALSE}
# general setup 

CheckCatch<-TRUE
DepVar<-"Hook_Count"  # dependent variable to be accumulated
PixelsTotal <- rep(0,nrow(Cbed_rules))     # generate vector of zeros for N pixels for map of total effort
EffortTimeSeries<-NULL  # accumulation of effort for each fishery for later aggregating into a single time series
KeepVars<-c("Split_Year")

Resolution<-4 # km2  of pixels

removeLastYear<-TRUE
includeZeroCatch<-TRUE
plotYlog<-FALSE
YtickMajor<-5000
YtickMinor<-1000
YtickMinorN<-YtickMajor/YtickMinor-1

XtickMajor<-10
XtickMinor<-1
XtickMinorN<-XtickMajor/XtickMinor-1

Xlimits<-c(1970,2020)
```


```{r Toothfish_LL, echo=FALSE}

TF<-3  # Target Fishery = toothfish  ### could be vector
DI<-Depth_intervals  # for altering depth intervals as needed for individual taxa

DistRules <- fnSetupCatchDistRules(  # apply rules given depths
   dLine
  ,DI
  ,Cbed_rules
  ,AreaGroups
  ,MEASOareas[,"Code"]
  ,ASDareas[,"Code"]
) # end fn call

####################################################
# determine total effort by rules

EffortByRules<-lapply(seq(1,length(DistRules),1),function(c,CD,dCSB,tf,DV,CheckCatch){  # rule#, ruleList,dataset,target fishery
  subCSB<-dCSB[CD[[c]]$Subset,]
  Effort<-subCSB[which(subCSB[,"TFN"] %in% tf),DV]
  if(CheckCatch){
      Catch<-subCSB[which(subCSB[,"TFN"] %in% tf),"Catch"]
      return(data.frame(Effort           = sum(Effort[!is.na(Effort)])
                       ,CatchTotal       = sum(Catch)
                       ,CatchNotNAEffort = sum(Catch[!is.na(Effort)]) ))
      } else { # end if CheckCatch
       return(data.frame(Effort = sum(Effort[!is.na(Effort)])))
      } #end else
},DistRules,dLine,TF,DepVar,CheckCatch)

EffortByRules<-bind_rows(EffortByRules)

####################################################
# distribute catches to pixels
Pixels    <- rep(0,nrow(Cbed_rules))     # generate vector of zeros for N pixels
RuleZeroArea<-NULL
for(c in seq(1,length(DistRules),1)){ # too memory intensive to do lapply
  if(DistRules[[c]]$Area_km2!=0){
    Density   <- EffortByRules[c,"Effort"]/DistRules[[c]]$Area_km2        # density per km2
    # place value in each relevant pixel according to CbedAreaSubset multiplying by Cbed[,"Area"]
    Pixels[DistRules[[c]]$CbedAreaSubset] <- 
      Pixels[DistRules[[c]]$CbedAreaSubset] + 
      Density*Resolution  # in order that sum of pixels in an area gives the correct quantity  
  } else {
    RuleZeroArea<-c(RuleZeroArea,c,EffortByRules[c,"Effort"])
  }
} # end loop c

cat(cat("Total effort in Bulletin for fishery ("),cat(TF_Plot_Order[which(TF_Plot_Order[,"TFn"] %in% TF),"TXN_Code"],sep=", "),cat("): ", sum(EffortByRules[,"Effort"])),"\n",sep="")
cat("     Proportion of Catch with Effort Records: ",(sum(EffortByRules[,"CatchNotNAEffort"])/sum(EffortByRules[,"CatchTotal"])),"\n",sep="")

cat("Effort allocated to pixels: ",sum(Pixels),"\n",sep="") 
if(!is.null(RuleZeroArea)){
cat("Rules with zero area and effort not allocated\n")
print.data.frame(as.data.frame(matrix(RuleZeroArea,ncol=2,byrow=TRUE,dimnames = list(NULL,c("Rule","Effort")))))
} else {
 cat("No areas had rules with zero area, and effort not allocated\n\n") 
}

# combine with other densities

PixelsTotal<-PixelsTotal+Pixels
```

### generate results
```{r , echo=FALSE}
#############################################
# Effort by MEASO area over time

Res<-bind_rows(lapply(seq(1,length(DistRules),1),fnDistributeDepVar,DistRules,dLine,TF,DepVar,KeepVars))

####################################################
# check all records are accounted for

if(nrow(Res)!=nrow(dLine)) {cat("Only ",nrow(Res)/nrow(dLine)*100,"% Bulletin records selected by rules.\n\n",sep="")} else {
  cat("All records from Bulletin selected by application of the rules.\n\n")
}

# add records to total
EffortTimeSeries<-bind_rows(EffortTimeSeries,Res)


```
  
```{r,echo=FALSE}
# plot time series of bird by-catch
plotYlog<-FALSE

BirdByCatch<-aggregate(BirdCatchData[,"By.Catch"],list(BirdCatchData[,"Sector"],BirdCatchData[,"Year"]),sum,na.rm=TRUE)
dimnames(BirdByCatch)[[2]]<-c("Sector","Year","Catch")
BirdByCatch[BirdByCatch[,"Year"]<2000 & BirdByCatch[,"Catch"]==0,"Catch"]<-NA
BirdByCatch<-bind_cols(data.frame(Fleet = rep("Legal",nrow(BirdByCatch))),BirdByCatch)

BirdIUU<-aggregate(BirdCatchData[,"IUU"],list(BirdCatchData[,"Sector"],BirdCatchData[,"Year"]),sum,na.rm=TRUE)
dimnames(BirdIUU)[[2]]<-c("Sector","Year","Catch")
BirdIUU[(BirdIUU[,"Year"]<2000 | BirdIUU[,"Year"]>2007) & BirdIUU[,"Catch"]==0,"Catch"]<-NA
BirdIUU<-bind_cols(data.frame(Fleet = rep("IUU",nrow(BirdIUU))),BirdIUU)

pdf<-bind_rows(BirdByCatch,BirdIUU)

# assign uncertainty to points to use as point size in plots
pdf<-bind_cols(pdf,data.frame(Uncertainty=rep(0.5,nrow(pdf))))
selRows<-pdf[,"Fleet"]=="Legal" & 
        ( (pdf[,"Sector"]=="Central Indian" & pdf[,"Year"]>=2002) | 
          (pdf[,"Sector"]=="Atlantic" & pdf[,"Year"]>=1994) |
          (pdf[,"Sector"]=="West Pacific" & pdf[,"Year"]>=1998)
        ) # end selection  
pdf[selRows,"Uncertainty"]<-1

PlotVar<-"Catch"

maxY<-max(pdf[!is.na(pdf[,PlotVar]),PlotVar])
minY<-min(pdf[!is.na(pdf[,PlotVar]),PlotVar])

if(plotYlog){
  Ylimits<-c(10^floor(log10(minY)),10^ceiling(log10(maxY)))
} else {
  YmaxVals<-fnYmax(maxY)
  Ylimits<-c(0,YmaxVals[1])
  YtickMajor<-YmaxVals[2]
}

pdf$Sector<-factor(pdf$Sector) 
Sector<-pdf$Sector
pdf$Fleet<-factor(pdf$Fleet,levels =c("Legal","IUU"))
Fleet<-pdf$Fleet



Xlimits<-c(floor(min(pdf[,"Year"])/10)*10,ceiling(max(pdf[,"Year"])/10)*10)


p<-ggplot() 
p<-p +scale_x_continuous(minor_breaks = seq(Xlimits[1],Xlimits[2],by=XtickMinor), breaks = seq(Xlimits[1],Xlimits[2],by=XtickMajor), limits = Xlimits)
if (plotYlog) {
  p <- p + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),labels = trans_format("log10", math_format(10^.x)), limits = Ylimits) + annotation_logticks(sides="l")
} else {
  p<-p +scale_y_continuous(breaks = seq(Ylimits[1],Ylimits[2],by=YtickMajor), minor_breaks = seq(Ylimits[1],Ylimits[2],by=YtickMinor), limits = Ylimits, labels = scales::comma)
  }
p <- p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()
               ,panel.background = element_blank()
               , axis.line = element_line(colour = "black",size=1, linetype="solid")
               ,axis.ticks.length=unit(0.25,"cm")
               ,legend.key.width = unit(1,"cm")
               )#end theme
p<- p+ geom_line(pdf, mapping = (aes(x = pdf[,"Year"], y = pdf[,PlotVar], col = Sector, lty = Fleet)), show.legend=TRUE)
p<- p+ geom_point(pdf, mapping = (aes(x = pdf[,"Year"], y = pdf[,PlotVar], col = Sector,size=Uncertainty)), show.legend=TRUE)
p<-p+scale_size(name = "Uncertainty",breaks = c(0.5,1),limits = c(0.5,1),range = c(1,2),labels = c("High","Low"))

p <- p + labs(x = "Year", y ="By-Catch", title="Seabird by-catch by sector")

p<-p + scale_colour_manual(values=MEASOsectors[match(unique(pdf[,"Sector"]),MEASOsectors[,"Name"]),"Colour"])
p<-p + scale_linetype_manual(values=c("solid","dashed"))
p

ggsave("IMAF.tiff",width = 15,height = 10, units = "cm")
```

# References    
.     
